%% GeometryModellingTutorial.tex
%%
%%
\documentclass[a4paper,12pt]{article}

\usepackage[T1]{fontenc} 
\usepackage{ucs} 
\usepackage[utf8x]{inputenc} 
%%french%%\usepackage[frenchb]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{verbatim}
\usepackage{moreverb}
\usepackage{fancyvrb}
\usepackage{alltt} 
\usepackage{eurosym} 
\usepackage{hyperref}
\usepackage{colortbl}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{pgf}
\usepackage{float} 

\addtolength{\textwidth}{+2cm}
\addtolength{\textheight}{+3cm}
\addtolength{\topmargin}{-1.5cm}
\addtolength{\oddsidemargin}{-1cm}

\newcommand{\basepath}{.}
\newcommand{\imagepath}{\basepath/images}
\newcommand{\codingpath}{\basepath/coding}
\newcommand{\pdftextpath}{\basepath/pdftex_t}
\newcommand{\pdftexpath}{\basepath/pdftex}

\input{include/Software_declare_verbatim.tex}

\newcommand{\pn}{\par\noindent}
\newcommand{\TT}[1]{"\texttt{#1}"}

\title{Geometry modelling with \texttt{geomtools}\\%
{\small{(Software/geomtools/GeometryModellingTutorial -- version 0.1)}}}
\author{F. Mauger <\texttt{mauger@lpccaen.in2p3.fr}>}
\date{2011-12-01}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

\begin{abstract}
In this note, we explain the principles and tools
for modelling a virtual geometry setup within \texttt{geomtools}.
\end{abstract}

\tableofcontents

\section{Introduction}

\pn  The \texttt{geomtools} program  library provides  some high-level
general  purpose  utility classes  and  embedded  algorithms to  build
virtual geometry models in a  somewhat easy way.  It has been designed
as  the main  tool for  feeding  external programs  with a  standalone
geometry description, using some automated exporting/filtering tools to
interface with these third-party programs and libraries. In the fields
of experimental  high energy and  nuclear physics, those  programs are
typically in charge of :
\begin{itemize}
\item the simulation of particle tracks through the
virtual  geometry model  of  a  detector  (GEANT4),  
\item reconstruction  algorithm,
\item visualization software,
\item various step of the data analysis. 
\end{itemize}
Unfortunately, there  is not one  single generic and standard  tool or
even  paradigm  to achieve  such  functionnalities. Usually,  software
libraries  use their  own geometry  modelling scheme,  with  their own
strategy, optimization and various policies  that can make them non or
hardly interoperable.   Particularly, the choice  for such a  tool can
prevent the user of client application to use in parallel another tool
with different modeling techniques.

\pn  Because of  this,  we have  implemented  some geometry  modelling
interface (GMI)  and tools  that, we hope,  are supposed to  allow the
making  of new  interfaces  compatible with  other geometry  modelling
implementations.   Of  course,  there   is  no   hope  to   cover  all
functionnalities  you  could   dream  about.   However,  the  geometry
modelling tools  in \texttt{geomtools}  try to address  most practical
cases  in the  framework  of our  experimental  activities :  detector
simulation, visualization, reconstruction and data analysis.

\pn  The  \texttt{geomtools} GMI  relies  on  some standard  modelling
approach that  have intrinsic limitations. Any  virtual geometry model
managed by  \texttt{geomtools} uses a hierarchical  system to describe
the  physical 3D-objects  in a  geometry  setup.  It  deals only  with
placement of daughter objects in their mother volume at several levels
of  a possibly  large hierarchy.  There  is no  possibility to  handle
overlapping   volumes  or  complex   nested  geometries   with  cyclic
mother/daughter  relationship. This  apporach  is shared  by the  GDML
language, the GEANT4 and ROOT libraries which are compatible with this
paradigm.  So  it is  expected that \texttt{geomtools}  will interface
naturally with these implementations.

\vskip 5mm
\pn
Subversion repository:\\
\texttt{https://nemo.lpc-caen.in2p3.fr/svn/geomtools/}
\pn
DocDB reference: \texttt{NemoDocDB-doc-1995}
\pn
References: see also
\textit{Geometry mapping with \texttt{geomtools}} (\texttt{NemoDocDB-doc-1996})
\pagebreak

\input{basic_concepts.tex}

\clearpage
\input{use_cases.tex}

\clearpage

\section{Conclusion}

\pn To be done.

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% end of GeometryModellingTutorial.tex
