%% DatatoolsContainerTutorial.tex
%%
%%
\documentclass[a4paper,12pt]{article}

\usepackage[T1]{fontenc}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{verbatim}
\usepackage{moreverb}
\usepackage{fancyvrb}
\usepackage{alltt}
\usepackage{eurosym}
\usepackage{hyperref}
\usepackage{colortbl}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{pgf}
\usepackage{float}

\addtolength{\textwidth}{+2cm}
\addtolength{\textheight}{+3cm}
\addtolength{\topmargin}{-1.5cm}
\addtolength{\oddsidemargin}{-1cm}

\newcommand{\basepath}{.}
\newcommand{\imagepath}{\basepath/images}
\newcommand{\codingpath}{\basepath/coding}
\newcommand{\pdftextpath}{\basepath/pdftex_t}
\newcommand{\pdftexpath}{\basepath/pdftex}

\input{include/Software_declare_verbatim.tex}

\newcommand{\pn}{\par\noindent}
\newcommand{\TT}[1]{"\texttt{#1}"}

\title{Using container objects in datatools\\%
%{\small{(Software/DatatoolsContainerTutorial -- datatools version 5.0.0)}}}
{\small{(datatools version 5.0.0)}}}
\author{F. Mauger <\texttt{mauger@lpccaen.in2p3.fr}>}
\date{2013-04-22}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle

\begin{abstract}
This note  explains how to use  the container classes  provided by the
\texttt{datatools} program library.
\end{abstract}

\tableofcontents

\section{Introduction}

\pn  The  \texttt{datatools}  program library  provides  among  other
components     a    couple     of     container    classes,     namely
\texttt{datatools::properties},   \texttt{datatools::multi\_properties}
and \texttt{datatools::things} classes.

\vskip 5mm
\pn
Subversion repository:\\
\texttt{https://nemo.lpc-caen.in2p3.fr/svn/datatools/} \\
in the \texttt{doc/Memos/DatatoolsContainerTutorial} subdirectory
\pn
DocDB reference: \texttt{NemoDocDB-doc-1997}
\pn
References: see also \textit{Serialization with the \texttt{datatools} program library}
(\texttt{NemoDocDB-doc-2003})

\clearpage

\input{properties_howto.tex}
\clearpage

\input{multi_properties_howto.tex}
\clearpage

\input{things_howto.tex}
\clearpage

\section{Conclusion}

\pn  Three foundation container  classes have  been presented  in this
note :

\begin{itemize}

\item  The  \texttt{datatools::properties}  class  can be  used  as  a
  container   for  configuration   parameters  for   complex  objects,
  algorithms  or application  programs.  It can  also  be used  within
  classes by object composition to serve as a versatile and extensible
  store for arbitrary data. It provides ASCII human friendly formatted
  I/O functionalities.

\item The  \texttt{datatools::multi\_properties} class can  be used to
  handle  a   complex  set  of   \emph{configurations}  objects,  each
  configuration implements a \texttt{datatools::properties} object and
  is  stored within a  named \emph{section}.  It provides  ASCII human
  friendly formatted I/O functionalities.

\item A \texttt{datatools::things}  object is a versatile non-copyable
  container for arbitrary \emph{serializable}  objects. It can be used
  as the core container for some complex data model.

\end{itemize}

All three classes are serializable with the native Boost/Serialization
system.


\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% end of DatatoolsContainerTutorial.tex
